This is TeX, Version 3.14159 (Web2C 7.3.1) (format=latex 2000.6.29)  14 OCT 2003 11:07
**eigen-3
(eigen-3.tex
LaTeX2e <1999/12/01> patch level 1
Babel <v3.6Z> and hyphenation patterns for american, french, german, ngerman, n
ohyphenation, loaded.
(/usr/statlocal/teTeX/share/texmf/tex/latex/seminar/seminar.cls
Document Class: seminar 1997/10/13, 1.4
Document Style: `seminar' v1.4 <1997/10/13> (tvz)
\slidewidth=\dimen102
\slideheight=\dimen103
\footheight=\dimen104
(/usr/statlocal/teTeX/share/texmf/tex/latex/base/article.cls
Document Class: article 1999/09/10 v1.4a Standard LaTeX document class
(/usr/statlocal/teTeX/share/texmf/tex/latex/base/size10.clo
File: size10.clo 1999/09/10 v1.4a Standard LaTeX file (size option)
)
\c@part=\count79
\c@section=\count80
\c@subsection=\count81
\c@subsubsection=\count82
\c@paragraph=\count83
\c@subparagraph=\count84
\c@figure=\count85
\c@table=\count86
\abovecaptionskip=\skip41
\belowcaptionskip=\skip42
\bibindent=\dimen105
)
(/usr/statlocal/teTeX/share/texmf/tex/latex/seminar/sem-page.sty)
\before@document=\toks14
\after@document=\toks15
\before@enddocument=\toks16
\c@slide=\count87
\slide@count=\count88
\@slidebox=\box26
\not@slidebox=\box27
\slide@hook=\toks17
\after@slide=\toks18
\slide@footins=\insert233
\slide@listdepth=\count89
\saved@specials=\box28
\before@newslide=\toks19
\after@slidepage=\toks20
\slidesep=\skip43
\slideframewidth=\dimen106
\slideframesep=\dimen107
\semin=\dimen108
\semcm=\dimen109
)
(/usr/statlocal/teTeX/share/texmf/tex/latex/config/seminar.con)
(/home/SLOTH/brian/tex/texinput/bj.sty
\c@nbct=\count90
\c@assumption=\count91
\c@defn=\count92
\c@lemma=\count93
\c@theorem=\count94
\c@proposition=\count95
\c@claim=\count96
\c@corollary=\count97
\c@@example=\count98
)
(/usr/statlocal/teTeX/share/texmf/tex/latex/localstyles/txr/txfonts.sty
Package: txfonts 2000/12/15 v3.1
LaTeX Font Info:    Redeclaring symbol font `operators' on input line 14.
LaTeX Font Info:    Overwriting symbol font `operators' in version `normal'
(Font)                  OT1/cmr/m/n --> OT1/txr/m/n on input line 14.
LaTeX Font Info:    Overwriting symbol font `operators' in version `bold'
(Font)                  OT1/cmr/bx/n --> OT1/txr/m/n on input line 14.
LaTeX Font Info:    Overwriting symbol font `operators' in version `bold'
(Font)                  OT1/txr/m/n --> OT1/txr/bx/n on input line 15.
\symitalic=\mathgroup4
LaTeX Font Info:    Overwriting symbol font `italic' in version `bold'
(Font)                  OT1/txr/m/it --> OT1/txr/bx/it on input line 19.
LaTeX Font Info:    Redeclaring math alphabet \mathrm on input line 21.
LaTeX Font Info:    Redeclaring math alphabet \mathbf on input line 22.
LaTeX Font Info:    Overwriting math alphabet `\mathbf' in version `normal'
(Font)                  OT1/cmr/bx/n --> OT1/txr/bx/n on input line 22.
LaTeX Font Info:    Overwriting math alphabet `\mathbf' in version `bold'
(Font)                  OT1/cmr/bx/n --> OT1/txr/bx/n on input line 22.
LaTeX Font Info:    Redeclaring math alphabet \mathit on input line 23.
LaTeX Font Info:    Overwriting math alphabet `\mathit' in version `normal'
(Font)                  OT1/cmr/m/it --> OT1/txr/m/it on input line 23.
LaTeX Font Info:    Overwriting math alphabet `\mathit' in version `bold'
(Font)                  OT1/cmr/bx/it --> OT1/txr/m/it on input line 23.
LaTeX Font Info:    Overwriting math alphabet `\mathit' in version `bold'
(Font)                  OT1/txr/m/it --> OT1/txr/bx/it on input line 24.
LaTeX Font Info:    Redeclaring math alphabet \mathsf on input line 33.
LaTeX Font Info:    Overwriting math alphabet `\mathsf' in version `normal'
(Font)                  OT1/cmss/m/n --> OT1/txss/m/n on input line 33.
LaTeX Font Info:    Overwriting math alphabet `\mathsf' in version `bold'
(Font)                  OT1/cmss/bx/n --> OT1/txss/m/n on input line 33.
LaTeX Font Info:    Overwriting math alphabet `\mathsf' in version `bold'
(Font)                  OT1/txss/m/n --> OT1/txss/b/n on input line 34.
LaTeX Font Info:    Redeclaring math alphabet \mathtt on input line 43.
LaTeX Font Info:    Overwriting math alphabet `\mathtt' in version `normal'
(Font)                  OT1/cmtt/m/n --> OT1/txtt/m/n on input line 43.
LaTeX Font Info:    Overwriting math alphabet `\mathtt' in version `bold'
(Font)                  OT1/cmtt/m/n --> OT1/txtt/m/n on input line 43.
LaTeX Font Info:    Overwriting math alphabet `\mathtt' in version `bold'
(Font)                  OT1/txtt/m/n --> OT1/txtt/b/n on input line 44.
LaTeX Font Info:    Redeclaring symbol font `letters' on input line 51.
LaTeX Font Info:    Overwriting symbol font `letters' in version `normal'
(Font)                  OML/cmm/m/it --> OML/txmi/m/it on input line 51.
LaTeX Font Info:    Overwriting symbol font `letters' in version `bold'
(Font)                  OML/cmm/b/it --> OML/txmi/m/it on input line 51.
LaTeX Font Info:    Overwriting symbol font `letters' in version `bold'
(Font)                  OML/txmi/m/it --> OML/txmi/bx/it on input line 52.
\symlettersA=\mathgroup5
LaTeX Font Info:    Overwriting symbol font `lettersA' in version `bold'
(Font)                  U/txmia/m/it --> U/txmia/bx/it on input line 60.
LaTeX Font Info:    Redeclaring symbol font `symbols' on input line 70.
LaTeX Font Info:    Overwriting symbol font `symbols' in version `normal'
(Font)                  OMS/cmsy/m/n --> OMS/txsy/m/n on input line 70.
LaTeX Font Info:    Overwriting symbol font `symbols' in version `bold'
(Font)                  OMS/cmsy/b/n --> OMS/txsy/m/n on input line 70.
LaTeX Font Info:    Overwriting symbol font `symbols' in version `bold'
(Font)                  OMS/txsy/m/n --> OMS/txsy/bx/n on input line 71.
\symAMSa=\mathgroup6
LaTeX Font Info:    Overwriting symbol font `AMSa' in version `bold'
(Font)                  U/txsya/m/n --> U/txsya/bx/n on input line 87.
\symAMSb=\mathgroup7
LaTeX Font Info:    Overwriting symbol font `AMSb' in version `bold'
(Font)                  U/txsyb/m/n --> U/txsyb/bx/n on input line 96.
\symsymbolsC=\mathgroup8
LaTeX Font Info:    Overwriting symbol font `symbolsC' in version `bold'
(Font)                  U/txsyc/m/n --> U/txsyc/bx/n on input line 106.
LaTeX Font Info:    Redeclaring symbol font `largesymbols' on input line 113.
LaTeX Font Info:    Overwriting symbol font `largesymbols' in version `normal'
(Font)                  OMX/cmex/m/n --> OMX/txex/m/n on input line 113.
LaTeX Font Info:    Overwriting symbol font `largesymbols' in version `bold'
(Font)                  OMX/cmex/m/n --> OMX/txex/m/n on input line 113.
LaTeX Font Info:    Overwriting symbol font `largesymbols' in version `bold'
(Font)                  OMX/txex/m/n --> OMX/txex/bx/n on input line 114.
\symlargesymbolsA=\mathgroup9
LaTeX Font Info:    Overwriting symbol font `largesymbolsA' in version `bold'
(Font)                  U/txexa/m/n --> U/txexa/bx/n on input line 122.
LaTeX Info: Redefining \not on input line 1036.
)
(/usr/statlocal/teTeX/share/texmf/tex/latex/graphics/epsfig.sty
Package: epsfig 1999/02/16 v1.7a (e)psfig emulation (SPQR)

(/usr/statlocal/teTeX/share/texmf/tex/latex/graphics/graphicx.sty
Package: graphicx 1999/02/16 v1.0f Enhanced LaTeX Graphics (DPC,SPQR)

(/usr/statlocal/teTeX/share/texmf/tex/latex/graphics/keyval.sty
Package: keyval 1999/03/16 v1.13 key=value parser (DPC)
\KV@toks@=\toks21
)
(/usr/statlocal/teTeX/share/texmf/tex/latex/graphics/graphics.sty
Package: graphics 1999/02/16 v1.0l Standard LaTeX Graphics (DPC,SPQR)

(/usr/statlocal/teTeX/share/texmf/tex/latex/graphics/trig.sty
Package: trig 1999/03/16 v1.09 sin cos tan (DPC)
)
(/usr/statlocal/teTeX/share/texmf/tex/latex/config/graphics.cfg)
Package graphics Info: Driver file: dvips.def on input line 80.

(/usr/statlocal/teTeX/share/texmf/tex/latex/graphics/dvips.def
File: dvips.def 1999/02/16 v3.0i Driver-dependant file (DPC,SPQR)
))
\Gin@req@height=\dimen110
\Gin@req@width=\dimen111
)
\epsfxsize=\dimen112
\epsfysize=\dimen113
)
(/home/SLOTH/brian/tex/texinput/multicol.sty
Style option: `multicol' v1.4m <92/09/04> (FMi)
English documentation          <92/09/04> (FMi)
\mult@box=\box29
\multicol@leftmargin=\dimen114
\c@unbalance=\count99
\c@collectmore=\count100
\c@tracingmulticols=\count101
\col@number=\count102
\doublecol@number=\count103
\multicoltolerance=\count104
\multicolpretolerance=\count105
\full@width=\dimen115
\page@free=\dimen116
\premulticols=\dimen117
\postmulticols=\dimen118
\multicolsep=\skip44
\multicolbaselineskip=\skip45
\partial@page=\box30
\last@line=\box31
) (eigen-3.aux)
\openout1 = `eigen-3.aux'.

LaTeX Font Info:    Checking defaults for OML/txmi/m/it on input line 53.
LaTeX Font Info:    Try loading font information for OML+txmi on input line 53.


(/usr/statlocal/teTeX/share/texmf/tex/latex/localstyles/txr/omltxmi.fd
File: omltxmi.fd 2000/12/15 v3.1
)
LaTeX Font Info:    ... okay on input line 53.
LaTeX Font Info:    Checking defaults for T1/cmr/m/n on input line 53.
LaTeX Font Info:    ... okay on input line 53.
LaTeX Font Info:    Checking defaults for OT1/cmr/m/n on input line 53.
LaTeX Font Info:    ... okay on input line 53.
LaTeX Font Info:    Checking defaults for OMS/txsy/m/n on input line 53.
LaTeX Font Info:    Try loading font information for OMS+txsy on input line 53.


(/usr/statlocal/teTeX/share/texmf/tex/latex/localstyles/txr/omstxsy.fd
File: omstxsy.fd 2000/12/15 v3.1
)
LaTeX Font Info:    ... okay on input line 53.
LaTeX Font Info:    Checking defaults for OMX/txex/m/n on input line 53.
LaTeX Font Info:    Try loading font information for OMX+txex on input line 53.


(/usr/statlocal/teTeX/share/texmf/tex/latex/localstyles/txr/omxtxex.fd
File: omxtxex.fd 2000/12/15 v3.1
)
LaTeX Font Info:    ... okay on input line 53.
LaTeX Font Info:    Checking defaults for U/txexa/m/n on input line 53.
LaTeX Font Info:    Try loading font information for U+txexa on input line 53.

(/usr/statlocal/teTeX/share/texmf/tex/latex/localstyles/txr/utxexa.fd
File: utxexa.fd 2000/12/15 v3.1
)
LaTeX Font Info:    ... okay on input line 53.
LaTeX Font Info:    Try loading font information for OT1+txr on input line 53.

(/usr/statlocal/teTeX/share/texmf/tex/latex/localstyles/txr/ot1txr.fd
File: ot1txr.fd 2000/12/15 v3.1
)
LaTeX Font Info:    Try loading font information for U+txmia on input line 57.

(/usr/statlocal/teTeX/share/texmf/tex/latex/localstyles/txr/utxmia.fd
File: utxmia.fd 2000/12/15 v3.1
)
LaTeX Font Info:    Try loading font information for U+txsya on input line 57.

(/usr/statlocal/teTeX/share/texmf/tex/latex/localstyles/txr/utxsya.fd
File: utxsya.fd 2000/12/15 v3.1
)
LaTeX Font Info:    Try loading font information for U+txsyb on input line 57.

(/usr/statlocal/teTeX/share/texmf/tex/latex/localstyles/txr/utxsyb.fd
File: utxsyb.fd 2000/12/15 v3.1
)
LaTeX Font Info:    Try loading font information for U+txsyc on input line 57.

(/usr/statlocal/teTeX/share/texmf/tex/latex/localstyles/txr/utxsyc.fd
File: utxsyc.fd 2000/12/15 v3.1
)
LaTeX Font Info:    Try loading font information for OMS+txr on input line 61.

(/usr/statlocal/teTeX/share/texmf/tex/latex/localstyles/txr/omstxr.fd
File: omstxr.fd 2000/12/15 v3.1
)
LaTeX Font Info:    Font shape `OMS/txr/m/n' in size <10> not available
(Font)              Font shape `OMS/txsy/m/n' tried instead on input line 61.
\slidebox@1=\box32
LaTeX Font Info:    Font shape `OMS/txr/m/n' in size <9> not available
(Font)              Font shape `OMS/txsy/m/n' tried instead on input line 92.
LaTeX Font Info:    Try loading font information for OT1+txtt on input line 104
.

(/usr/statlocal/teTeX/share/texmf/tex/latex/localstyles/txr/ot1txtt.fd
File: ot1txtt.fd 2000/12/15 v3.1
)
[1

]

LaTeX Warning: Slide 5 overfull by 8.41246pt on input line 246.

\slidebox@2=\box33
[2] [3]
Overfull \hbox (1.28386pt too wide) in paragraph at lines 355--355
[]\OT1/txtt/m/n/5 Residual standard error: 1.172 on 27 degrees of freedom[]
 []


Overfull \hbox (6.53383pt too wide) in paragraph at lines 355--355
[]\OT1/txtt/m/n/5 Multiple R-Squared: 0.7527,     Adjusted R-squared: 0.652[]
 []


Overfull \hbox (1.28386pt too wide) in paragraph at lines 355--355
[]\OT1/txtt/m/n/5 F-statistic: 7.472 on 11 and 27 DF,  p-value: 1.051e-05[]
 []

[4]
File: scree-cor.ps Graphic file (type eps)
 <scree-cor.ps>
Overfull \hbox (1.44836pt too wide) in paragraph at lines 415--418
[]
 []


LaTeX Warning: Slide 10 overfull by 16.00175pt on input line 426.


Overfull \vbox (6.90178pt too high) has occurred while \output is active []



LaTeX Warning: Slide 11 overfull by 2.036pt on input line 533.


LaTeX Warning: Slide 12 overfull by 10.61894pt on input line 590.


Overfull \vbox (4.85532pt too high) has occurred while \output is active []

\slidebox@3=\box34
\slidebox@4=\box35

[5] [6]
Overfull \hbox (15.66878pt too wide) in paragraph at lines 637--637
[]\OT1/txtt/m/n/9 > biplot(pc.cor$scores[,1:2],pc.cor$loadings[,1:2],ylabs=name
s(X))[]
 []

File: biplot-highway.ps Graphic file (type eps)
<biplot-highway.ps>

LaTeX Warning: Slide 16 overfull by 15.35796pt on input line 643.


Overfull \vbox (15.35796pt too high) has occurred while \output is active []


[7]
File: highway-scores.ps Graphic file (type eps)
 <highway-scores.ps> [8]

LaTeX Warning: Slide 18 overfull by 2.26413pt on input line 707.


LaTeX Warning: Slide 19 overfull by 2.4766pt on input line 727.

[9]

LaTeX Warning: Slide 21 overfull by 7.28792pt on input line 787.

[10]
Overfull \hbox (8.52904pt too wide) detected at line 876
| \OML/txmi/m/it/10 N \OT1/txr/m/n/10 = [\OML/txmi/m/it/10 n[]\OT1/txr/m/n/10 ]
 = []  [] [] []\OML/txmi/m/it/10 R \OT1/txr/m/n/10 = [\OML/txmi/m/it/10 n[]=n\O
T1/txr/m/n/10 ] = []  [] [] []\OML/txmi/m/it/10 C \OT1/txr/m/n/10 = [\OML/txmi/
m/it/10 n[]=n\OT1/txr/m/n/10 ] = []
 []


LaTeX Warning: Slide 23 overfull by 6.9044pt on input line 889.

[11] [12]
Overfull \hbox (1.28386pt too wide) in paragraph at lines 1005--1005
[]\OT1/txtt/m/n/5 +                     c("Rare","Abundant","V. Abund."))[]
 []


LaTeX Warning: Slide 26 overfull by 14.19395pt on input line 1014.


Overfull \vbox (6.07903pt too high) has occurred while \output is active []


[13] (eigen-3.aux) )
Here is how much of TeX's memory you used:
 1863 strings out of 10901
 20976 string characters out of 72060
 75480 words of memory out of 263001
 4800 multiletter control sequences out of 10000+0
 23408 words of font info for 71 fonts, out of 400000 for 1000
 14 hyphenation exceptions out of 1000
 32i,10n,22p,216b,518s stack positions out of 300i,100n,500p,50000b,4000s

Output written on eigen-3.dvi (13 pages, 36616 bytes).